---
title: "20190729_scID_cleancode"
author: "Sam N"
date: "29/07/2019"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::install_github("BatadaLab/scID")
library(scID)
library(Matrix)
library(Seurat)
library(dplyr)
library(cowplot)
#(install.packages("biomod2"))
library(biomod2)

if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("MAST")
library(MAST)
```

```{r read in files and format}
Carter_gem<-read.table("~/Desktop/Example_data/scIDCarter/Final/20190702exprmatCarterREFGEM.tsv", header = T, stringsAsFactors = T)
rownames(Carter_gem) = make.unique(as.character(Carter_gem[, 1]))
rownames(Carter_gem)

reference_clusters <- readRDS(file="~/Desktop/Example_data/scIDCarter/Final/20190709CartRefClusCharPopsManFAC.rds")

target_gem <- readRDS (file="~/Desktop/Example_data/scIDCarter/Final/20190705TargetNaylerGEMMouseids.rds")
names(target_gem)[names(target_gem) == "MGI.symbol"] <- "gene"
rownames(target_gem) = make.unique(as.character(target_gem[, 1]))
rownames(target_gem)

```

```{r run scID}

scID_outputCarterNayler <- scid_multiclass(target_gem = target_gem, reference_gem = Carter_gem, reference_clusters = reference_clusters, estimate_weights_from_target = FALSE)



```



```{r outputs}
make_heatmap(gem = Carter_gem, labels = reference_clusters, markers = scID_outputCarterNayler$markers)

make_heatmap(gem = target_gem, labels = scID_outputCarterNayler$labels, markers = scID_outputCarterNayler$markers)

scID_outputCarterNayler$labels

(table(scID_outputCarterNayler4$markers$cluster))

write.csv (scID_outputCarterNayler$labels, file = "~/Desktop/Example_data/scIDCarter/Final/20190730a.csv")

CarterIDs20190730a<-read.csv("~/Desktop/Example_data/scIDCarter/Final/20190730a.csv", header = T)

organoids.combined@meta.data$CarterIDs20190730a <- CarterIDs20190730a
#Note only 954 cells have been placed with this new method, this is causing problems to plot. Let's try Katerinas 
#p1 <-DimPlot(organoids.combined, reduction = "umap", group.by = "dataname")
#p2 <-DimPlot(organoids.combined, reduction = "umap", label = TRUE)
#plot_grid (p1,p2)
```

``{Katerinas way to vis cells}
organoids.combined@meta.data$scID.ident =as.factor(CarterIDs20190730a)
organoids.combined@meta.data$scID.ident = as.factor(scID_outputCarterNayler$labels[rownames(organoids.combined@meta.data)])
DimPlot(organoids.combined, group.by = organoids.combined@meta.data$scID.ident)

```





```

```{r restrict markers}

markers = scID_outputCarterNayler$markers
#Then you can view it as all data frame structures 
View(markers)
 
#Below is a code to filter these markers and rerun scID with a subset of top50 positive markers and top50 negative markers
 
library(dplyr)
positive_markers <- markers[which(markers$avg_logFC > 0), ]
top50_positive <- positive_markers %>% group_by(cluster) %>% top_n(n = 50, wt = avg_logFC)
negative_markers <- markers[which(markers$avg_logFC < 0), ]
top50_negative <- negative_markers %>% group_by(cluster) %>% top_n(n = 50, wt = avg_logFC)
 
top100_markers <- rbind(top50_negative, top50_positive)

scID_outputCarterNayler2 <- scid_multiclass(target_gem = target_gem, reference_gem = Carter_gem, reference_clusters = reference_clusters, markers = top100_markers, estimate_weights_from_target = FALSE)
```

#Need to think up a better way to visualize/enumerate the clusters on a background!
#Would be nice to run on cluster as quite computationally intensive
#Would be nice to know what the genes contributing to the marker signatures are rather than x20340


