---
title: "20190730Pearson_cleancode"
author: "Sam N"
date: "30/07/2019"
output: html_document
---
```{r read in data}
ctrl.data<-Read10X(data.dir ="/Users/samnayler/Desktop/bsg-ftp.well.ox.ac.uk/additional_analyses/10X-hashing/NAY6153A2/hashing.sng/", gene.column = 1)
#Note not sure if these have actually been demultiplexed

ctrl<-CreateSeuratObject(counts = ctrl.data, project = "organoids", min.cells = 3, min.features = 200)
ctrl$stim <- "CTRL"
ctrl<-subset(ctrl, subset = nFeature_RNA > 500)
ctrl<-NormalizeData(ctrl, verbose = FALSE)
ctrl<-FindVariableFeatures(ctrl, selection.method = "vst", nFeatures =1000)


#https://satijalab.org/seurat/v3.0/interaction_vignette.html
#https://satijalab.org/seurat/v3.0/sctransform_vignette.html

#need to check the norm/qc/filtering

# Set up stimulated object
mg.data<-Read10X(data.dir ="/Users/samnayler/Desktop/bsg-ftp.well.ox.ac.uk/additional_analyses/10X-hashing/NAY6153A1/hashing.sng/", gene.column = 1)

mg<-CreateSeuratObject(counts = mg.data, project = "organoids", min.cells = 3, min.features = 200)
mg$stim <- "STIM"
mg<-subset(mg, subset = nFeature_RNA > 500)
mg<-NormalizeData(mg, verbose = FALSE)
mg<-FindVariableFeatures(mg, selection.method = "vst", nFeatures =1000)
```

```{r Find integration anchors}
organoid.anchors<-FindIntegrationAnchors(object.list = list(ctrl, mg), dims = 1:20)
organoids.combined<- IntegrateData(anchorset = organoid.anchors, dims = 1:20)
DefaultAssay(organoids.combined) <-"integrated"
organoids.combined<-ScaleData(organoids.combined, verbose = FALSE)
organoids.combined<-RunPCA (organoids.combined, npcs = 30, verbose = FALSE)
organoids.combined <-RunUMAP (organoids.combined, reduction = "pca", dims = 1:12)
organoids.combined<-FindNeighbors(organoids.combined, reduction = "pca", dims = 1:20)
#NOTE I SHOULD CONSIDER USING SCTRANSFORM, which replaces normalizedata, scaledata and findvariablefeatures. This could also affect my population markers, DE and also the affinity of scID. Could be important!
```

```{r find clusters}
organoids.combined<-FindClusters(organoids.combined, resolution = 0.5)
p1 <-DimPlot(organoids.combined, reduction = "umap", group.by = "stim")
p2 <-DimPlot(organoids.combined, reduction = "umap", label = TRUE)
plot_grid (p1,p2)
```

```{r derive average expression}
aveexpnayler<-AverageExpression(organoids.combined)
aveexpnayler.df<-as.data.frame(aveexpnayler$RNA)
aveexpnayler.df$gene<-rownames(aveexpnayler.df)
hvgnayler<-as.character(aveexpnayler.df$gene)


mart1 = useMart(biomart = "ENSEMBL_MART_ENSEMBL", host="www.ensembl.org", path = "/biomart/martservice", dataset="hsapiens_gene_ensembl")
mart2 = useMart(biomart = "ENSEMBL_MART_ENSEMBL", host="www.ensembl.org", path = "/biomart/martservice", dataset="mmusculus_gene_ensembl")

orth.humantue <-getLDS(attributes=c("hgnc_symbol"),
       filters="hgnc_symbol", values=hvgnayler, mart=mart1,
       attributesL=c("mgi_symbol"), martL=mart2, filtersL = "with_hsapiens_homolog", valuesL = T)
       
mergednaylermouseorth<-merge(aveexpnayler.df, orth.humantue, by.x="gene", by.y="HGNC.symbol")
mergednaylermouseorth<-mergednaylermouseorth[-1]

#But these are not hvgs?! They are just avg expression. wrong if they are based off organoids.combined which is based on top 2000 hvg.

#What about below?

```

```{r get carter data read in}
Carter.raw.data2<-Read10X(data.dir = "/Users/samnayler/Desktop/Example_data/scIDCarter/annotated_Unnormdata/")
CarterUnnorm<-CreateSeuratObject(counts = Carter.raw.data2, project = "scID", min.cells = 3, min.features = 200)

GetAssay(CarterUnnorm, assay = "RNA")
#Assay data with 20661 features for 77458 cells
cart<-subset(CarterUnnorm, subset = nFeature_RNA > 500)
cart<-NormalizeData(cart, verbose = FALSE)
cart<-FindVariableFeatures(cart, selection.method = "vst", nFeatures =2000)
#Should I be using 1000 or 2000 here? Lets try 2000 as I think its what was used for organoids.combined

cart<-ScaleData(cart, verbose = FALSE)
cart<-RunPCA (cart, npcs = 30, verbose = FALSE)
cart<-RunUMAP (cart, reduction = "pca", dims = 1:12)
cart<-FindNeighbors(cart, reduction = "pca", dims = 1:20)

cart<-FindClusters(cart, resolution = 1.8)
p1 <-DimPlot(cart, reduction = "umap", group.by = "seurat_clusters")
p2 <-DimPlot(cart, reduction = "umap", label = TRUE)
plot_grid (p1,p2)
```

aveexpcarter<-AverageExpression(cart)
#But will this be based on the clustering I have done (47 pops, not their clustering ie 48 pops and half the cells)
aveexpcarter.df<-as.data.frame(aveexpcarter$RNA)
aveexpcarter.df$gene<-rownames(aveexpcarter.df)
hvgcarter<-as.character(aveexpcarter.df$gene)
#But these are not hvgs?! They are just avg expression
hvgnayler<-as.character(aveexpnayler.df$gene)


#Move the MGI.symbol to the first column
mergednaylermouseorth2<-
mergednaylermouseorth %>%
  select (MGI.symbol, everything())
  
  
aveexpcarter.df2<-
aveexpcarter.df %>%
  select (gene, everything())
  
onion2<-merge(mergednaylermouseorth, aveexpcarter.df2, by.x="MGI.symbol", by.y="gene")
  

onion3<-onion2[-1]
cor(onion3, use="complete.obs", method = "pearson")
cornaylerumap10popvscarter47pop<-cor(onion3, use="complete.obs", method = "pearson")

#try and plot
library(reshape2)
melted_cormat <- melt(cornaylerumap10popvscarter47pop)
head(melted_cormat)

library(ggplot2)
ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()
#This works, need to see if I can run it on hvg

```

```{r do with top variable genes}

#change this code below but get variable genes

GetAssayData(organoids.combined@assays$integrated)

naylerintegrated<-GetAssayData(organoids.combined@assays$integrated)

naylerintegrated


aveexpnayler_integrated<-AverageExpression(organoids.combined)
aveexpnayler_integrated.df<-as.data.frame(aveexpnayler$integrated)
aveexpnayler_integrated.df$gene<-rownames(aveexpnayler_integrated.df)
hvgnayler_integrated<-as.character(aveexpnayler_integrated.df$gene)

mart1 = useMart(biomart = "ENSEMBL_MART_ENSEMBL", host="www.ensembl.org", path = "/biomart/martservice", dataset="hsapiens_gene_ensembl")
mart2 = useMart(biomart = "ENSEMBL_MART_ENSEMBL", host="www.ensembl.org", path = "/biomart/martservice", dataset="mmusculus_gene_ensembl")

hvgnayler_integrated_asmouse <-getLDS(attributes=c("hgnc_symbol"),
       filters="hgnc_symbol", values=hvgnayler_integrated, mart=mart1,
       attributesL=c("mgi_symbol"), martL=mart2, filtersL = "with_hsapiens_homolog", valuesL = T)

#1767 out of 2000 genes with homology

mergednayler_intergrated_mouseorth<-merge(aveexpnayler_integrated.df, hvgnayler_integrated_asmouse, by.x="gene", by.y="HGNC.symbol")

mergednayler_intergrated_mouseorth<-mergednayler_intergrated_mouseorth[-1]

#This is now my list of hvg and ave expression values  with identifiable homology from nayler organoids that have mouse probe ids. I now need to merge this with the carter values and retain just these genes

#Move the MGI.symbol to the first column
mergednayler_intergrated_mouseorth<-
mergednayler_intergrated_mouseorth %>%
  select (MGI.symbol, everything())

head(aveexpcarter)
?

mergedcarterfullnaylerhvg<-merge(mergednayler_intergrated_mouseorth, aveexpcarter.df, by.x="MGI.symbol", by.y="gene")
head(mergedcarterfullnaylerhvg)
#What has happened to the gene symbols here?
#I have 1708 genes remaining

mergedcarterfullnaylerhvg2<-mergedcarterfullnaylerhvg[-1]
corhvgnayler11popvscarter47pop<-cor(mergedcarterfullnaylerhvg2, use="complete.obs", method = "pearson")


#try and plot
library(reshape2)
melted_cormat_hvg <- melt(corhvgnayler11popvscarter47pop)
head(melted_cormat_hvg)

library(ggplot2)
ggplot(data = melted_cormat_hvg, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()
```



```{r try and repeat pearson correlation with cell types}

#Lets try and merge the metadata with the cell type classification ie reference clusters
#Should actually probably merge the cell types inside a file first first


#cartmeta<-read.csv("~/Desktop/Example_data/scIDCarter/cerebellum_cell_metadata.tsv", header = T, sep = "")
#colnames(CarterUnnorm)
#Note that the seurat object does not have -1 after it

#CartMeta<-CarterUnnorm@meta.data

#If I can merge cartmeta with the rownames from cartunnorm I can isolate just the utilized cells with their corresponding cell type


#carterlots<-as.data.frame(colnames(CarterUnnorm)(CarterUnnorm$orig.ident))
#This doesnt have a title! Need one to merge it
#carterlots<-as.data.frame(carterlots)

#mergie<-merge(carterlots, carts, by.x="colnames(CarterUnnorm)", by.y="colnames(CarterUnnorm)")
#STOPPED HERE MONDAY 29/07 - need to wrangle this data into more useful format to merge it and rerun pearson correlation


#One of the things I can try is to pull in the cells present in the metadata (cartmeta) file and have everything else return an NA value. Then I can add that list as a metadata column. 

#subsetz<-subset(CarterUnnorm, subset = metadatacell = not N/A)
```

rmarkdown::render ('20190702_OrganoidsseuratV3.Rmd', output_format = 'pdf_document')




