---
title: "20190729_scID_cleancode"
author: "Sam N"
date: "29/07/2019"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::install_github("BatadaLab/scID")
library(scID)
library(Matrix)
library(Seurat)
library(dplyr)
library(cowplot)
#(install.packages("biomod2"))
library(biomod2)

if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("MAST")
library(MAST)
```

```{r read in files and format}
Carter_gem<-read.table("~/Desktop/Example_data/scIDCarter/Final/20190702exprmatCarterREFGEM.tsv", header = T, stringsAsFactors = T)
rownames(Carter_gem) = make.unique(as.character(Carter_gem[, 1]))
rownames(Carter_gem)

reference_clusters <- readRDS(file="~/Desktop/Example_data/scIDCarter/Final/20190709CartRefClusCharPopsManFAC.rds")

target_gem <- readRDS (file="~/Desktop/Example_data/scIDCarter/Final/20190705TargetNaylerGEMMouseids.rds")
names(target_gem)[names(target_gem) == "MGI.symbol"] <- "gene"
rownames(target_gem2) = make.unique(as.character(target_gem[, 1]))
rownames(target_gem)

target_gem2<-target_gem2[,-1]


```

```{r run scID}

#scID_outputCarterNayler <- scid_multiclass(target_gem = target_gem2, reference_gem = Carter_gem, reference_clusters = reference_clusters, estimate_weights_from_target = FALSE)

scID_outputCarterNayler2<- scid_multiclass(target_gem = target_gem3, reference_gem = Carter_gem, reference_clusters = reference_clusters, logFC = 0.3, only_pos = FALSE, estimate_weights_from_target = TRUE,normalize_reference=FALSE)

```



```{r outputs}
table(scID_outputCarterNayler3$labels)
(table(scID_outputCarterNayler3$markers$cluster))
length(scID_outputCarterNayler3$labels)


make_heatmap(gem = Carter_gem, labels = reference_clusters, markers = scID_outputCarterNayler3$markers)

make_heatmap(gem = target_gem3, labels = scID_outputCarterNayler3$labels, markers = scID_outputCarterNayler3$markers)



markers = scID_outputCarterNayler3$markers

write.csv (scID_outputCarterNayler3$labels, file = "~/Desktop/Example_data/scIDCarter/Final/20190802_05.csv")
write.csv (scID_outputCarterNayler3$markers, file = "~/Desktop/Example_data/scIDCarter/Final/20190802_05_markers.csv")

#CarterIDs20190801a<-read.csv("~/Desktop/Example_data/scIDCarter/Final/20190801a.csv", header = T)


organoids.combined@meta.data$CarterIDs2019080205 <- scID_outputCarterNayler3$labels
p1 <-DimPlot(organoids.combined, reduction = "umap", group.by = "CarterIDs2019080205")
p2 <-DimPlot(organoids.combined, reduction = "umap", label = TRUE)
p3 <-DimPlot(organoids.combined, reduction = "umap", label = TRUE, group.by = "CarterIDs20190801b")
plot_grid (p1,p2, p3)
#Should explore here the option for plotting/labelling of cells
```

``{Katerinas way to vis cells}
#organoids.combined@meta.data$scID.ident = as.factor(scID_outputCarterNayler2$labels[rownames(organoids.combined@meta.data)])


#DimPlot(organoids.combined, reduction = "umap", group.by = organoids.combined@meta.data$scID.ident)
#This doesnt work but try this simpler version
DimPlot(organoids.combined, reduction = "umap", group.by = "scID.ident")
DimPlot(organoids.combined, reduction = "umap", group.by = "scID.ident", label = TRUE)
#This is very close - what if I can replace the numerical factors with the cell type names(I would ideally also have the time printed in)

#For some reason this doesnt currently work, neither does my plotting strategy. This may be to do the fact that scID did not pick all cells.
#What if I need to subset the cells or reset the idents?
Idents(object = organoids.combined, cells = 1:2512) <- "scID.ident"


#What if I used the pipe function to lookup the corresponding cell name/developmental age from the number data. I could then add that as a metadata column and project that 
head(organoids.combined@meta.data$scID.ident)
#[1] 22 21 35 18 22 35
#Levels: 1 10 11 12 13 14 15 16 17 18 19 2 20 21 22 23 24 25 26 27 28 29 3 30 31 32 33 34 35 36 37 38 39 4 40 41 42 43 44 45 46 47 48 5 7 9 unassigned
#Note populations 6 & 8 do not appear in this list? No matched cells?
Cartpopsunique<-read.csv("/Users/samnayler/Desktop/Example_data/scIDCarter/20190717CartersPopulationsUnique.csv")

#simplest way may be a merge
scID_outputCarterNayler3labels.df<-as.data.frame(scID_outputCarterNayler3$labels)

head(scID_outputCarterNayler3labels.df)
#                   scID_outputCarterNayler2$labels
#AAACCTGAGGTACTCT_1                              22
#AAACCTGAGTGGACGT_1                              21
#AAACCTGTCAGAAATG_1                              35
#AAACCTGTCTCGGACG_1                              18
#AAACGGGAGTACATGA_1                              22
#AAACGGGAGTGTACTC_1                              35

head(Cartpopsunique)
# sample_id cluster_id  cell_type
#1      E14A         31 Astrocytes
#2      E14B         31 Astrocytes
#3      E15A         31 Astrocytes
#4      E15B         31 Astrocytes
#5      E16A         31 Astrocytes
#6      E16B         31 Astrocytes


#Use VLOOKUP to pull out a concatenated string of time, sample rep and cell type as well as just sample cell type. Try and add to metadata

write.csv(scID_outputCarterNayler3labels.df, file = "/Users/samnayler/Desktop/Example_data/scIDCarter/Final/20190802_05scid3restricted.csv")
#Can use my VLOOKUP exel script to pull out the according cell types and then read these to metadata columns and plot
#Need to cut the excel part out here

vlooked<-read.csv("~/Desktop/Example_data/scIDCarter/Final/20190805scID3_restricted_CartersPopulationsUniqueVLOOKUPS.csv", header = T)
vlooked$scID_20190802_05
organoids.combined@meta.data$CarterIDs20190802_05_celltypes <- vlooked$scID_20190802_05
p9<-DimPlot(organoids.combined, reduction = "umap", group.by = "CarterIDs20190802_05_celltypes", label = TRUE)
plot_grid(p2,p9)

#now try and add long entries with time/rep info
organoids.combined@meta.data$CarterIDs20190802_05_celltypes_long <- vlooked$scID_20190802_05_long

p10<-DimPlot(organoids.combined, reduction = "umap", group.by = "CarterIDs20190802_05_celltypes", label = TRUE, label.size = 1.5)
plot_grid(p2,p10)



write.csv(organoids.combined@meta.data, file='~/Desktop/20190802metadataorganoidscombined_seuratV3.csv', sep ="/t")
#stopped here friday 02082019
#To do next week
#Update seurat object, trial sctnorm, rerun scID, pearsons with clean data/merge with hvg from filtered carter, work on cleaning projections

```
```{resume monday 0508}
#Have updated some of the code above to produce plots of analysis ran overnight 0208
#How to plot dots as symbols? 

p10<-DimPlot(organoids.combined, reduction = "umap", group.by = "CarterIDs20190802_05_celltypes", label = TRUE, label.size = 1.5, repel = TRUE)

p11<-DimPlot(organoids.combined, reduction = "umap", group.by = "CarterIDs20190802_05_celltypes_long", label = TRUE, label.size = 2, shape.by = "CarterIDs20190802_05_celltypes", repel = TRUE)

#Warning messages:
#1: The shape palette can deal with a maximum of 6
#discrete values because more than 6 becomes difficult
#to discriminate; you have 15. Consider specifying
#shapes manually if you must have them. 
#2: Removed 1394 rows containing missing values (geom_point).


 p12<-DimPlot(organoids.combined, reduction = "umap", group.by = "CarterIDs20190802_05_celltypes", label = TRUE, label.size = 1.5, shape.by = "CarterIDs20190802_05_celltypes_long")
#Nice plot, decompressing similar cell types in carter in separate plots
nlevels(celltypez)


#p14<-DimPlot(organoids.combined, reduction = "umap", group.by = "CarterIDs20190802_05_celltypes", label = TRUE, label.size = 1.5, do.return = TRUE)






#One fix will be to examine facet plots! This might be very nice!

#p10 + geom_jitter(aes(color=CarterIDs20190802_05_celltypes), size = 2, show.legend = FAL~SE) + facet_wrap(~CarterIDs20190802_05_celltypes)

#Revisit this

```



```

```{r restrict markers}

markers = scID_outputCarterNayler$markers
#Then you can view it as all data frame structures 
View(markers)
 
#Below is a code to filter these markers and rerun scID with a subset of top50 positive markers and top50 negative markers
 
library(dplyr)
positive_markers <- markers[which(markers$avg_logFC > 0), ]
top50_positive <- positive_markers %>% group_by(cluster) %>% top_n(n = 50, wt = avg_logFC)
negative_markers <- markers[which(markers$avg_logFC < 0), ]
top50_negative <- negative_markers %>% group_by(cluster) %>% top_n(n = 50, wt = avg_logFC)
 
top100_markers <- rbind(top50_negative, top50_positive)

scID_outputCarterNayler3 <- scid_multiclass(target_gem = target_gem3, reference_gem = Carter_gem, reference_clusters = reference_clusters, markers = top100_markers, estimate_weights_from_target = TRUE)
```

```{r better way to pull out gems}
ExportToCellbrowser(carter_sct, "wd", dataset.name = "20190807Carter_SCT",reductions = "umap", markers.file = NULL, cluster.field = "Cluster", cb.dir = NULL, port = NULL, skip.expr.matrix = FALSE, skip.metadata = FALSE, skip.reductions = FALSE)

carter_sct_gem<-read.table("~/Desktop/0190807_carter_sct_exprmatrix/exprMatrix.tsv.gz", header = T)
#stopped here 0807, still need to process the SCT data 

```


```{r try new gem extraction for running SCT data in scID}
#Read in reference clusters from carter
reference_clusters <- readRDS(file="~/Desktop/Example_data/scIDCarter/Final/20190709CartRefClusCharPopsManFAC.rds")

#getExpr must be outdated
#I could try the following
newgmatrsct<-as.matrix(GetAssayData(newganoids.combined))
head(newgmatrsct)
humangenes<-as.character(rownames(newgmatrsct))
#WILL NEED TO CONVERT TO MOUSE
dim(newgmatrsct)
 dim(newgmatrsct)
 # 17176  1653
mart1 = useMart(biomart = "ENSEMBL_MART_ENSEMBL", host="www.ensembl.org", path = "/biomart/martservice", dataset="hsapiens_gene_ensembl")
mart2 = useMart(biomart = "ENSEMBL_MART_ENSEMBL", host="www.ensembl.org", path = "/biomart/martservice", dataset="mmusculus_gene_ensembl")

newganoids_sct_asmouse <-getLDS(attributes=c("hgnc_symbol"),
       filters="hgnc_symbol", values=humangenes, mart=mart1,
       attributesL=c("mgi_symbol"), martL=mart2, filtersL = "with_hsapiens_homolog", valuesL = T)

head(newganoids_sct_asmouse)
#  HGNC.symbol MGI.symbol
#1      ZNF772       Zfy1
#2       LMCD1      Lmcd1
#3        PCNT       Pcnt
#4       KIF24      Kif24
#5      MT-CO2     mt-Co2
#6      FLVCR2     Flvcr2
dim(newganoids_sct_asmouse)
#13782     2

w<-as.data.frame(newgmatrsct)
dim(w)
w2 <- cbind(genes = rownames(w), w)
dim(w2)


newganoids_sct_asmouse2<-merge(newganoids_sct_asmouse, w2, by.x="HGNC.symbol", by.y="genes")


head(newganoids_sct_asmouse2)
dim(newganoids_sct_asmouse2)
colnames(newganoids_sct_asmouse2)
rownames(newganoids_sct_asmouse2)

newganoids_sct_asmouse3<-newganoids_sct_asmouse2[,-1]
rownames(newganoids_sct_asmouse3) = make.unique(newganoids_sct_asmouse3[, 1])
newganoids_sct_asmouse4<-newganoids_sct_asmouse3[,-1]



#At the same time I do this I should consider trying a pearson correlation with all genes?

cartermatr_sct<-as.matrix(GetAssayData(carter_sct))





scID_outputCarterNayler_sct0815<- scid_multiclass(target_gem = newganoids_sct_asmouse4, reference_gem = cartermatr_sct, reference_clusters = reference_clusters, logFC = 0.3, only_pos = FALSE, estimate_weights_from_target = TRUE,normalize_reference=FALSE)



table(scID_outputCarterNayler_sct0815$labels)
(table(scID_outputCarterNayler_sct0815$markers$cluster))
length(scID_outputCarterNayler_sct0815$markers$labels)


scID_outputCarterNayler_sct0815hm<-make_heatmap(gem = cartermatr_sct, labels = reference_clusters, markers = scID_outputCarterNayler_sct0815$markers)

scID_outputCarterNayler_sct0815hm2<-make_heatmap(gem = newganoids_sct_asmouse4, labels = scID_outputCarterNayler_sct0815$labels, markers = scID_outputCarterNayler_sct0815$markers)



markers = scID_outputCarterNayler_sct0815$markers

write.csv (scID_outputCarterNayler_sct0815$labels, file = "~/Desktop/Example_data/scIDCarter/SCT/20190815.csv")
write.csv (scID_outputCarterNayler_sct0815$markers, file = "~/Desktop/Example_data/scIDCarter/SCT/20190815_markers.csv")



newganoids.combined@meta.data$CarterIDs20190815_sct <- scID_outputCarterNayler_sct0815$labels
p1 <-DimPlot(newganoids.combined, reduction = "umap", group.by = "CarterIDs20190815_sct")
p2 <-DimPlot(newganoids.combined, reduction = "umap", label = TRUE)
p3 <-DimPlot(newganoids.combined, reduction = "umap", label = TRUE, group.by = "CarterIDs20190815_sct")
plot_grid (p1,p2, p3)

#If I want to look at these in greater detail I need to add metadata columns with VLOOKUP ....p12<-DimPlot(newganoids.combined, reduction = "umap", group.by = "cell_type", label = TRUE, label.size = 1.5)

#shape.by?




#####try restricting markers overnight
positive_markers <- markers[which(markers$avg_logFC > 0), ]
top50_positive <- positive_markers %>% group_by(cluster) %>% top_n(n = 50, wt = avg_logFC)
negative_markers <- markers[which(markers$avg_logFC < 0), ]
top50_negative <- negative_markers %>% group_by(cluster) %>% top_n(n = 50, wt = avg_logFC)
 
top100_markers <- rbind(top50_negative, top50_positive)

scID_outputCarterNayler_sct0815b<- scid_multiclass(target_gem = newganoids_sct_asmouse4, reference_gem = cartermatr_sct, reference_clusters = reference_clusters, logFC = 0.3, only_pos = FALSE, estimate_weights_from_target = TRUE,normalize_reference=FALSE, markers =top100_markers)
####stopped here thurs, need to produce output for this and solve plotting issue

table(scID_outputCarterNayler_sct0815b$labels)
(table(scID_outputCarterNayler_sct0815b$markers$cluster))
length(scID_outputCarterNayler_sct0815b$markers$labels)


scID_outputCarterNayler_sct081b5hm<-make_heatmap(gem = cartermatr_sct, labels = reference_clusters, markers = scID_outputCarterNayler_sct0815b$markers)

scID_outputCarterNayler_sct0815bhm2<-make_heatmap(gem = newganoids_sct_asmouse4, labels = scID_outputCarterNayler_sct0815b$labels, markers = scID_outputCarterNayler_sct0815b$markers)
#I should examine whether I can modify the axis in ggplot etc


markers = scID_outputCarterNayler_sct0815b$markers

write.csv (scID_outputCarterNayler_sct0815b$labels, file = "~/Desktop/Example_data/scIDCarter/SCT/20190815b_markersrest.csv")
write.csv (scID_outputCarterNayler_sct0815b$markers, file = "~/Desktop/Example_data/scIDCarter/SCT/20190815b_markers_markersrest.csv")


#lets explore new visualisation strategies that contend with this complexity
newganoids.combined@meta.data$CarterIDs20190815b_sct <- scID_outputCarterNayler_sct0815b$labels
p1 <-DimPlot(newganoids.combined, reduction = "umap", group.by = "CarterIDs20190815b_sct")
#p1 is way too messy. If I can come up with a way to add a meta data column that allows me to show one cell type at a time in colour or with highlight this would be advantageous.
p2 <-DimPlot(newganoids.combined, reduction = "umap", label = TRUE)
p3 <-DimPlot(newganoids.combined, reduction = "umap", label = TRUE, group.by = "CarterIDs20190815b_sct")
plot_grid (p1,p2, p3)


VlnPlot(newganoids.combined, features ="percent.mt", split.by = "integrated_snn_res.0.8")


px <-DimPlot(newganoids.combined, reduction = "umap", group.by = "umaptest")
#What about an if then for 1, otherwise NA or 0.

#I can also try 
pzx1 <-DimPlot(newganoids.combined, reduction = "umap", group.by = "CarterIDs20190815b_sct", cols = c('1' = 'red', '2' = 'grey', '3' = 'grey', '4' = 'grey', '5' = 'grey', '6' = 'grey', '7' = 'grey', '8' = 'grey', '9' = 'grey', '10' = 'grey', '11' = 'grey', '12' = 'grey', '13' = 'grey', '14' = 'grey', '15' = 'grey', '16' = 'grey', '17' = 'grey', '18' = 'grey', '19' = 'grey', '20' = 'grey', '21' = 'grey', '22' = 'grey', '23' = 'grey', '24' = 'grey', '25' = 'grey', '26' = 'grey', '27' = 'grey', '28' = 'grey', '29' = 'grey', '30' = 'grey', '31' = 'grey', '32' = 'grey', '33' = 'grey', '34' = 'grey', '35' = 'grey', '36' = 'grey', '37' = 'grey', '38' = 'grey', '39' = 'grey', '40' = 'grey', '41' = 'grey', '42' = 'grey', '43' = 'grey', '44' ='grey','45' = 'grey', '46' = 'grey', '47' = 'grey', '48' ='grey', cells.highlight = '1'))
celllabel<-as.character(celltypesmega.char.alph[1])
pzx2<-pzx + labs(title =celllabel)
One<-plot_grid(pzx2,p2)
#This is not a bad sollution to my visualisation fix 
#Try and incorporate a lookup of celltypesmega.char.alph
#Can I overlay my pops on top of this?!?! Maybe as shapes?

#Useful but not necessary match("1", newganoids.combined@meta.data$CarterIDs20190815b_sct, nomatch = NA_integer_, incomparables = NULL)


#I can potentially filter/subset out and shapeby on cell type (as there should be 6 or fewer subdivisions?)

#Run through whole batch, also consider multiple colours to delineate related groups! Or symbols ;~D
pzx <-DimPlot(newganoids.combined, reduction = "umap", group.by = "CarterIDs20190815b_sct", cols = c('1' = 'grey', '2' = 'grey', '3' = 'grey', '4' = 'grey', '5' = 'grey', '6' = 'grey', '7' = 'grey', '8' = 'grey', '9' = 'grey', '10' = 'grey', '11' = 'grey', '12' = 'grey', '13' = 'grey', '14' = 'grey', '15' = 'grey', '16' = 'grey', '17' = 'grey', '18' = 'grey', '19' = 'grey', '20' = 'grey', '21' = 'grey', '22' = 'grey', '23' = 'grey', '24' = 'grey', '25' = 'grey', '26' = 'grey', '27' = 'grey', '28' = 'grey', '29' = 'grey', '30' = 'grey', '31' = 'grey', '32' = 'grey', '33' = 'grey', '34' = 'grey', '35' = 'grey', '36' = 'grey', '37' = 'grey', '38' = 'grey', '39' = 'grey', '40' = 'grey', '41' = 'grey', '42' = 'grey', '43' = 'grey', '44' ='grey','45' = 'grey', '46' = 'grey', '47' = 'grey', '48' ='red', cells.highlight = NULL))
celllabel<-as.character(celltypesmega.char.alph[48])
pzx<-pzx + labs(title =celllabel)
pzxplot<-plot_grid(pzx,p2)
pzxplot

####look at markers from LDA/SCID on SCT/restricted markers in heatmap
DefaultAssay(newganoids.combined) <- 'integrated'


scidLDAhm0919<-DoHeatmap(newganoids.combined, features = markers$gene, cells = 1:1653, group.by = "integrated_snn_res.0.8",
  group.bar = TRUE, disp.min = -2.5, disp.max = NULL,
  slot = "scale.data", assay = NULL, label = TRUE, size = 5.5,
  hjust = 0, angle = 45, raster = TRUE, draw.lines = TRUE,
  lines.width = NULL, group.bar.height = 0.02, combine = TRUE)
####

#Try and visualize related clusters simultaneously
#Astrocytes
grep("Astrocyte", celltypesmega.char.alph)


pzy <-DimPlot(newganoids.combined, reduction = "umap", group.by = "CarterIDs20190815b_sct", cols = c('1' = 'grey', '2' = 'grey', '3' = 'grey', '4' = 'grey', '5' = 'grey', '6' = 'grey', '7' = 'grey', '8' = 'grey', '9' = 'grey', '10' = 'grey', '11' = 'grey', '12' = 'grey', '13' = 'grey', '14' = 'grey', '15' = 'grey', '16' = 'grey', '17' = 'grey', '18' = 'grey', '19' = 'grey', '20' = 'grey', '21' = 'grey', '22' = 'grey', '23' = 'grey', '24' = 'grey', '25' = 'green', '26' = 'grey', '27' = 'grey', '28' = 'grey', '29' = 'blue', '30' = 'grey', '31' = 'orange', '32' = 'grey', '33' = 'grey', '34' = 'grey', '35' = 'grey', '36' = 'grey', '37' = 'grey', '38' = 'grey', '39' = 'grey', '40' = 'grey', '41' = 'grey', '42' = 'grey', '43' = 'grey', '44' ='grey','45' = 'grey', '46' = 'grey', '47' = 'grey', '48' ='grey', cells.highlight = NULL))
celllabel<-c(as.character(celltypesmega.char.alph[19]),as.character(celltypesmega.char.alph[25]), as.character(celltypesmega.char.alph[29]), as.character(celltypesmega.char.alph[31]))
celllabel2<-paste(celllabel, collapse = '')

pzy<-pzy + labs(title =celllabel2)
pzyplot<-plot_grid(pzy,p2)
pzyplot


pzyvasc <-DimPlot(newganoids.combined, reduction = "umap", group.by = "CarterIDs20190815b_sct", cols = c('1' = 'grey', '2' = 'grey', '3' = 'grey', '4' = 'grey', '5' = 'grey', '6' = 'grey', '7' = 'grey', '8' = 'grey', '9' = 'grey', '10' = 'grey', '11' = 'grey', '12' = 'grey', '13' = 'grey', '14' = 'red', '15' = 'grey', '16' = 'grey', '17' = 'grey', '18' = 'grey', '19' = 'grey', '20' = 'grey', '21' = 'grey', '22' = 'grey', '23' = 'grey', '24' = 'grey', '25' = 'grey', '26' = 'grey', '27' = 'grey', '28' = 'grey', '29' = 'grey', '30' = 'grey', '31' = 'grey', '32' = 'grey', '33' = 'orange', '34' = 'grey', '35' = 'grey', '36' = 'grey', '37' = 'grey', '38' = 'grey', '39' = 'grey', '40' = 'grey', '41' = 'grey', '42' = 'yellow', '43' = 'green', '44' ='grey','45' = 'blue', '46' = 'grey', '47' = 'violet', '48' ='brown', cells.highlight = NULL))
celllabel<- "Vasculature (014-Roof_plate-E10E11E12E13 , 033-Erythrocyte-E14E15E16E17P0P4P7P10, 042-Blood_vessel-E10E11E12E13E14E15E16E17P0P4P7P10, 043-Erythrocyte-E10E11E12E13E14E15, 045-Blood_vessel-E10E11E12E13E14E15E16E17P0P4P7P10, 046-Meninges/Pia_membrane-E11E12E13E14E15E16E17P0P4P7P10, 047-Ciliated_cells-E16E17P0P4P7P10, 048-Erythrocyte-E13E14E15E16E17P0P4P10"

pzyvasc<-pzyvasc + labs(title =celllabel)
pzyvascplot<-plot_grid(pzyvasc,p2)
pzyvascplot

#############
#Here I want to try and look simulatenously at the GABAergic progenitors and the DCN. Is it strange that Carter did not identify any GABAergic DCN?




####stopped here MOnday 08/19. Should work through remaning cells and also explor symbols etc

#####Now for further cells types with new colours

library("RColorBrewer")
display.brewer.all()
brewer.pal(n = 11, name = "RdBu")



pzyprog <-DimPlot(newganoids.combined, reduction = "umap", group.by = "CarterIDs20190815b_sct", cols = c('1' = 'grey', '2' = 'grey', '3' = '#FFC00', '4' = 'grey', '5' = 'grey', '6' = "#B2182B", '7' = 'grey', '8' = 'green', '9' = 'grey', '10' = 'grey', '11' = 'grey', '12' = 'grey', '13' = 'grey', '14' = 'grey', '15' = 'grey', '16' = '#F4A582', '17' = '#D1E5F0', '18' = '#FDDBC7', '19' = 'grey', '20' = '#92C5DE', '21' = 'grey', '22' = 'grey', '23' = 'grey', '24' = 'grey', '25' = 'grey', '26' = 'grey', '27' = 'grey', '28' = 'grey', '29' = 'grey', '30' = '#4393C3', '31' = 'grey', '32' = 'grey', '33' = 'grey', '34' = 'grey', '35' = 'grey', '36' = '#2166AC', '37' = 'grey', '38' = 'blue', '39' = 'grey', '40' = 'grey', '41' = 'grey', '42' = 'grey', '43' = 'grey', '44' ='grey','45' = 'grey', '46' = 'grey', '47' = 'grey', '48' ='grey', cells.highlight = NULL))
celllabel<- "Progenitors"

pzyprog<-pzyprog + labs(title =celllabel)
pzyprogplot<-plot_grid(pzyprog,p2)
pzyprogplot

grep("Granule", celltypesmega.char.alph)
 #[1]  2  4  7  9 10 11 13 21 22 26 32 37

pzygran <-DimPlot(newganoids.combined, reduction = "umap", group.by = "CarterIDs20190815b_sct", cols = c('1' = 'grey', '2' = "#B2182B", '3' = 'grey', '4' = "#67001F", '5' = 'grey', '6' = 'grey', '7' = "#D6604D", '8' = 'grey', '9' = "#F4A582", '10' = "#FDDBC7", '11' = 'orange', '12' = 'grey', '13' = "#D1E5F0", '14' = 'grey', '15' = 'grey', '16' = 'grey', '17' = 'grey', '18' = 'grey', '19' = 'grey', '20' = 'grey', '21' = "#92C5DE", '22' = "#4393C3", '23' = 'grey', '24' = 'grey', '25' = 'grey', '26' = "#2166AC", '27' = 'grey', '28' = 'grey', '29' = 'grey', '30' = 'grey', '31' = 'grey', '32' = "#053061", '33' = 'grey', '34' = 'grey', '35' = 'grey', '36' = 'grey', '37' = "red", '38' = 'grey', '39' = 'grey', '40' = 'grey', '41' = 'grey', '42' = 'grey', '43' = 'grey', '44' ='grey','45' = 'grey', '46' = 'grey', '47' = 'grey', '48' ='grey', cells.highlight = NULL))
celllabel<- "Granule cells"

pzygran<-pzygran + labs(title =celllabel)
pzygranplot<-plot_grid(pzygran,p2)
pzygranplot


####
grep("Glutamatergic", celltypesmega.char.alph)
#5 23 39

pzyglutdcn <-DimPlot(newganoids.combined, reduction = "umap", group.by = "CarterIDs20190815b_sct", cols = c('1' = 'grey', '2' = 'grey', '3' = 'grey', '4' = 'grey', '5' = 'red', '6' = 'grey', '7' = 'grey', '8' = 'grey', '9' = 'grey', '10' = 'grey', '11' = 'grey', '12' = 'grey', '13' = 'grey', '14' = 'grey', '15' = 'grey', '16' = 'grey', '17' = 'grey', '18' = 'grey', '19' = 'grey', '20' = 'grey', '21' = 'grey', '22' = 'grey', '23' = 'green', '24' = 'grey', '25' = 'grey', '26' = 'grey', '27' = 'grey', '28' = 'grey', '29' = 'grey', '30' = 'grey', '31' = 'grey', '32' = 'grey', '33' = 'grey', '34' = 'grey', '35' = 'grey', '36' = 'grey', '37' = "grey", '38' = 'grey', '39' = 'blue', '40' = 'grey', '41' = 'grey', '42' = 'grey', '43' = 'grey', '44' ='grey','45' = 'grey', '46' = 'grey', '47' = 'grey', '48' ='grey', cells.highlight = NULL))
celllabel<- "Glutamatergic DCN"

pzyglutdcn<-pzyglutdcn + labs(title =celllabel)
pzyglutdcnplot<-plot_grid(pzyglutdcn,p2)
pzyglutdcnplot

############
grep("GABA", celltypesmega.char.alph)
# 1 15 27 28 34 40

pzyGABA <-DimPlot(newganoids.combined, reduction = "umap", group.by = "CarterIDs20190815b_sct", cols = c('1' = 'red', '2' = 'grey', '3' = 'grey', '4' = 'grey', '5' = 'grey', '6' = 'grey', '7' = 'grey', '8' = 'grey', '9' = 'grey', '10' = 'grey', '11' = 'grey', '12' = 'grey', '13' = 'grey', '14' = 'grey', '15' = 'orange', '16' = 'grey', '17' = 'grey', '18' = 'grey', '19' = 'grey', '20' = 'grey', '21' = 'grey', '22' = 'grey', '23' = 'grey', '24' = 'grey', '25' = 'grey', '26' = 'grey', '27' = 'yellow', '28' = 'green', '29' = 'grey', '30' = 'grey', '31' = 'grey', '32' = 'grey', '33' = 'grey', '34' = 'blue', '35' = 'grey', '36' = 'grey', '37' = "grey", '38' = 'grey', '39' = 'grey', '40' = 'violet', '41' = 'grey', '42' = 'grey', '43' = 'grey', '44' ='grey','45' = 'grey', '46' = 'grey', '47' = 'grey', '48' ='grey', cells.highlight = NULL))
celllabel<- "GABAergic"

pzyGABA<-pzyGABA + labs(title =celllabel)
pzyGABAplot<-plot_grid(pzyGABA,p2)
pzyGABAplot

#######
#I should try and look at GABA and glut to check the localisation to my DCN/RL cluster - for this I will need to look at shades of colours...and or shapes



grep("Glutamatergic", celltypesmega.char.alph)
#5 23 39
grep("GABA", celltypesmega.char.alph)
# 1 15 27 28 34 40

pzyglutdcnandGABAprog <-DimPlot(newganoids.combined, reduction = "umap", group.by = "CarterIDs20190815b_sct", cols = c('1' = 'blue', '2' = 'grey', '3' = 'grey', '4' = 'grey', '5' = 'red', '6' = 'grey', '7' = 'grey', '8' = 'grey', '9' = 'grey', '10' = 'grey', '11' = 'grey', '12' = 'grey', '13' = 'grey', '14' = 'grey', '15' = 'blue', '16' = 'grey', '17' = 'grey', '18' = 'grey', '19' = 'grey', '20' = 'grey', '21' = 'grey', '22' = 'grey', '23' = 'red', '24' = 'grey', '25' = 'grey', '26' = 'grey', '27' = 'blue', '28' = 'blue', '29' = 'grey', '30' = 'grey', '31' = 'grey', '32' = 'grey', '33' = 'grey', '34' = 'blue', '35' = 'grey', '36' = 'grey', '37' = "grey", '38' = 'grey', '39' = 'red', '40' = 'blue', '41' = 'grey', '42' = 'grey', '43' = 'grey', '44' ='grey','45' = 'grey', '46' = 'grey', '47' = 'grey', '48' ='grey', cells.highlight = NULL))


celllabel<- "Glut DCN (red) and GABAergic prog (blue)"

pzyglutdcnandGABAprog<-pzyglutdcnandGABAprog + labs(title =celllabel)
pzyglutdcnandGABAprogplot<-plot_grid(pzyglutdcnandGABAprog,p2)
pzyglutdcnandGABAprogplot
#What else is localizing this the supposed Glutamatergic DCN/GCP/RLP cluster 


###
grep("GABA", celltypesmega.char.alph)
# 1 15 27 28 34 40
#PCS are 12
pzyPurkdcnandGABAprog <-DimPlot(newganoids.combined, reduction = "umap", group.by = "CarterIDs20190815b_sct", cols = c('1' = 'blue', '2' = 'grey', '3' = 'grey', '4' = 'grey', '5' = 'grey', '6' = 'grey', '7' = 'grey', '8' = 'grey', '9' = 'grey', '10' = 'grey', '11' = 'grey', '12' = 'purple', '13' = 'grey', '14' = 'grey', '15' = 'blue', '16' = 'grey', '17' = 'grey', '18' = 'grey', '19' = 'grey', '20' = 'grey', '21' = 'grey', '22' = 'grey', '23' = 'grey', '24' = 'grey', '25' = 'grey', '26' = 'grey', '27' = 'blue', '28' = 'blue', '29' = 'grey', '30' = 'grey', '31' = 'grey', '32' = 'grey', '33' = 'grey', '34' = 'blue', '35' = 'grey', '36' = 'grey', '37' = "grey", '38' = 'grey', '39' = 'grey', '40' = 'blue', '41' = 'grey', '42' = 'grey', '43' = 'grey', '44' ='grey','45' = 'grey', '46' = 'grey', '47' = 'grey', '48' ='grey', cells.highlight = NULL))


celllabel<- "Purkinje (purple) and GABAergic prog (blue)"

pzyPurkdcnandGABAprog<-pzyPurkdcnandGABAprog + labs(title =celllabel)
pzyPurkdcnandGABAprogplot<-plot_grid(pzyPurkdcnandGABAprog,p2)
pzyPurkdcnandGABAprogplot


#I need to plot via cell type grossly - perhaps here is where I can experiment with shape.by and color by

#######
pzyCilaCvsN <-DimPlot(newganoids.combined, reduction = "umap", group.by = "CarterIDs20190815b_sct", cols = c('1' = 'grey', '2' = 'grey', '3' = 'grey', '4' = 'grey', '5' = 'grey', '6' = 'grey', '7' = 'grey', '8' = 'grey', '9' = 'grey', '10' = 'grey', '11' = 'grey', '12' = 'grey', '13' = 'grey', '14' = 'grey', '15' = 'grey', '16' = 'grey', '17' = 'grey', '18' = 'grey', '19' = 'grey', '20' = 'grey', '21' = 'grey', '22' = 'grey', '23' = 'grey', '24' = 'grey', '25' = 'grey', '26' = 'grey', '27' = 'grey', '28' = 'grey', '29' = 'grey', '30' = 'grey', '31' = 'grey', '32' = 'grey', '33' = 'grey', '34' = 'grey', '35' = 'grey', '36' = 'grey', '37' = "grey", '38' = 'grey', '39' = 'grey', '40' = 'grey', '41' = 'grey', '42' = 'grey', '43' = 'grey', '44' ='grey','45' = 'grey', '46' = 'grey', '47' = 'red', '48' ='grey', cells.highlight = NULL), shape.by = 'integrated_snn_res.0.8')
celllabel<- "Nayler (ciliated ependymal cells) vs Carter ciliated cells"

pzyCilaCvsN<-pzyCilaCvsN + labs(title =celllabel)
pzyCilaCvsNplot<-plot_grid(pzyCilaCvsN,p2)
pzyCilaCvsNplot



#Try and get manual shaping

pzyCilaCvsN <-DimPlot(newganoids.combined, reduction = "umap", group.by = "CarterIDs20190815b_sct", cols = c('1' = 'grey', '2' = 'grey', '3' = 'grey', '4' = 'grey', '5' = 'grey', '6' = 'grey', '7' = 'grey', '8' = 'grey', '9' = 'grey', '10' = 'grey', '11' = 'grey', '12' = 'grey', '13' = 'grey', '14' = 'grey', '15' = 'grey', '16' = 'grey', '17' = 'grey', '18' = 'grey', '19' = 'grey', '20' = 'grey', '21' = 'grey', '22' = 'grey', '23' = 'grey', '24' = 'grey', '25' = 'grey', '26' = 'grey', '27' = 'grey', '28' = 'grey', '29' = 'grey', '30' = 'grey', '31' = 'grey', '32' = 'grey', '33' = 'grey', '34' = 'grey', '35' = 'grey', '36' = 'grey', '37' = "grey", '38' = 'grey', '39' = 'grey', '40' = 'grey', '41' = 'grey', '42' = 'grey', '43' = 'grey', '44' ='grey','45' = 'grey', '46' = 'grey', '47' = 'red', '48' ='grey', cells.highlight = NULL), shape.by = 'integrated_snn_res.0.8')






#### all the greys are grey
cols = c('1' = 'grey', '2' = 'grey', '3' = 'grey', '4' = 'grey', '5' = 'grey', '6' = 'grey', '7' = 'grey', '8' = 'grey', '9' = 'grey', '10' = 'grey', '11' = 'grey', '12' = 'grey', '13' = 'grey', '14' = 'grey', '15' = 'grey', '16' = 'grey', '17' = 'grey', '18' = 'grey', '19' = 'grey', '20' = 'grey', '21' = 'grey', '22' = 'grey', '23' = 'grey', '24' = 'grey', '25' = 'grey', '26' = 'grey', '27' = 'grey', '28' = 'grey', '29' = 'grey', '30' = 'grey', '31' = 'grey', '32' = 'grey', '33' = 'grey', '34' = 'grey', '35' = 'grey', '36' = 'grey', '37' = "grey", '38' = 'grey', '39' = 'grey', '40' = 'grey', '41' = 'grey', '42' = 'grey', '43' = 'grey', '44' ='grey','45' = 'grey', '46' = 'grey', '47' = 'grey', '48' ='grey', cells.highlight = NULL))

```
#Need to think up a better way to visualize/enumerate the clusters on a background!
#Would be nice to run on cluster as quite computationally intensive
#Would be nice to know what the genes contributing to the marker signatures are rather than x20340


